---
title: "monkeyr"
output: 
  md_document:
    variant: markdown_github
vignette: >
  %\VignetteIndexEntry{monkeyr vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Monkeyr 

The goal of `monkeyr` is to package up and share the R code needed to produce
flexdashboards and Rmarkdown reports from Monkeytronics monitoring data. The input 
data format is consistent with the Monkeytronics Sensor Node mobile app and web 
portal reporting functions. 

## Installation

Install the latest development version of monkeyr from github :

```{r, eval = FALSE}
# clone the repo and `Install and Restart`
# or `devtools::load_all()`

#remotes::install_bitbucket(repo = "monkeytronics/r-analytics", subdir = "monkeyr")
devtools::install_github("monkeytronics/monkeyr", build_vignettes = TRUE)
```

Monkeyr is structured as pure functions. The library dependencies are listed in the
`DESCRIPTION` file. This along with `roxygen` creates the `NAMESPACE` with all imports/exports.

## Example Set Up of an Rmd File (using home report example)

We start with a Monkeytronics Sensor Node data set :\cr

* obs.csv
* dev.csv
* weather.csv
* interv.csv

And we use the wrangling functions to create the following sanitised, wrangled data :

* `wrangled_obs`     : the joined data set
* `wrangled_devices` : devices list minus excluded devices
* `devices_for_map`  : a list used to populate a deployment map

(If you need to copy and paste this, make sure you remove `eval = FALSE`!)

```{r, eval = FALSE}
library(monkeyr)

wrangled_devices <- wrangle_devices(params$filtered_devices)

wrangled_weather <- wrangle_weather(params$filtered_weather)

wrangled_obs    <- wrangle_observations(
  filtered_obs   = params$filtered_obs,
  devices        = wrangled_devices,
  weather        = wrangled_weather
)

data_volume     <- get_data_volume(
  observations   = wrangled_obs,
  from_timestamp = params$fromTimeStamp,
  to_timestamp   = params$toTimeStamp
)

devices_for_map <- get_devices_for_map(
  devices        = wrangled_devices,
  data_volume    = data_volume
)

wrangled_devices<- remove_excluded_devices(
  target_data    = wrangled_devices,
  data_volume    = data_volume
)

wrangled_obs    <- remove_excluded_devices(
  target_data    = wrangled_obs,
  data_volume    = data_volume
)
```

Next, we can set some options for available data and colors:

```{r, eval = FALSE}
set_options(observations = wrangled_obs)
```

## Now Run Analysis Code (Home report example) 

We have everything we need to make a time series plot for humidity :

```{r, eval = FALSE}
ts_chart(
  observations = wrangled_obs,
  from_timestamp = test_params()$fromTimeStamp,
  to_timestamp = test_params()$toTimeStamp,
  target_variable = "hum"
)
```

or temperature :

```{r, eval = FALSE}
ts_chart(
  observations = wrangled_obs,
  from_timestamp = test_params()$fromTimeStamp,
  to_timestamp = test_params()$toTimeStamp,
  target_variable = "temp"
)
```

# Test Data & Params

We want to store dummy data sets in the package to speed up testing. There are 2
sources to consider. Firstly the raw csv files which we put into `dummy-data` 
and secondly the parameters which go in `dummy-params`.

```
├── inst
│   ├── dummy-data
│   │   ├── monkey_a
│   │   |   ├── dev.csv
│   │   |   ├── interv.csv
│   │   |   ├── obs.csv
│   │   |   ├── weather.csv
│   │   ├── monkey_b
│   │   |   ├── **.csv
│   ├── dummy-params
│   │   ├── params_blank.txt
│   │   ├── params_full_map.txt
│   │   ├── params_full_2vars.txt
│   │   ├── params_full_all.txt 
│   ├── rmd
│   │   ├── home.rmd
│   │   ├── my-report.rmd

```

# Testing your Flexdash Report in the Local Environment

During development of your flexdash report or for use with new datasets, 
you should put the rmd file into the inst/rmd folder. And add new data sets into 
`inst/dummy-data/{data-set-name}/*.csv`. Now you can test your code
using the `run_test_report` function. The following parameters are needed :

```{r, eval = FALSE}
run_test_report(
    report       = "home",           ## rmd file!
    dummy_data   = "monkey_a",       ## dummy data from inst/dummy-data
    dummy_params = "params_blank.txt"    ## dummy params from inst/dummy-params
)
```


The output will be generated as a html file in `html/{report}/{dummy_data}.html`


# Running an Analysis from inside a Docker Container

We have a function `?knit_report` that takes 
    - a list of parameters (paths to data and timestamps)  
    - output file name (so we can keep track of requests if needed)
    - output directory (we need this to tell the docker container where on the host to drop the files)

We run this like so:

```{r, eval = FALSE}
# the system.file calls are to access the example data installed with the package
# in production, the list of parameters will be generated by the script calling this
# report

  obs           <- "/tmp/obs.csv"
  dev           <- "/tmp/dev.csv"
  weather       <- "/tmp/weather.csv"
  interv        <- "/tmp/interv.csv"
  from          <- 1627639151
  to            <- 1630317551
  
  par_list <- monkeyr::make_params_list(
    filtered_obs           = obs,
    filtered_devices       = dev,
    filtered_weather       = weather,
    filtered_interventions = interv,
    fromTimeStamp          = from_ts,
    toTimeStamp            = to_ts
  )
  
  temporary_directory      <- Sys.getenv("TMPDIR", "/tmp")
  outfile                  <- file.path(temporary_directory, paste0("flexi", ".html"))

# knit with default file name and output dir
  monkeyr::knit_report(
    param_list = par_list,
    output_file = outfile,
    output_dir = temporary_directory,
    intermediates_dir = temporary_directory,
    envir = new.env()
  )
```

