---
title: "Indoor Environment Monitoring"
date: "`r format(Sys.time(), '%b %d %Y')`"

author:
  - name: "Saera Chun"
    affiliation: "He Kāinga Oranga, University of Otago"
    affiliation_url: https://www.healthyhousing.org.nz/
  - name: "Al Brennan"
    affiliation: "Monkeytronics, Wellington, NZ"
    affiliation_url: https://www.monkeytronics.co.nz/    

# orcid_id: 0000-0003-0645-5666
# bibliography: biblio.bib

output: 
  distill::distill_article:
    toc: true
    toc_depth: 2
    theme: theme.css

# paths with `inst` will only work in `dev` setting. 
# in `production` setting, please use real data
# or call installed files with `system.file`
# see example in `?knit_home_report()`
params:
  filtered_obs:             "../dummy-data/monkey_a/obs.csv"
  filtered_weather:         "../dummy-data/monkey_a/weather.csv"
  filtered_devices:         "../dummy-data/monkey_a/dev.csv"
  filtered_interventions:   "../dummy-data/monkey_a/interv.csv"
  report_params:            "-map-"                                            
  fromTimeStamp:            1627639151
  toTimeStamp:              1630317551
---

```{r setup, include=FALSE}
ENABLE_DEBUG <- FALSE

# load monkeyr package
library(monkeyr)
library(dplyr)
library(magrittr)
library(kableExtra)
library(ggplot2)

# other dependencies loaded through namespace
```


```{r WRANGLE_DATA, include=FALSE}

## STANDARD DATA WRANGLING & JOINING
## ---------------------------------

wrangled_devices <- monkeyr::wrangle_devices(params$filtered_devices)

wrangled_weather <- monkeyr::wrangle_weather(params$filtered_weather)

wrangled_obs <- monkeyr::wrangle_observations(
  filtered_obs   = params$filtered_obs,
  devices        = wrangled_devices,
  weather        = wrangled_weather
)

data_volume <- monkeyr::get_data_volume(
  observations   = wrangled_obs,
  from_timestamp = params$fromTimeStamp,
  to_timestamp   = params$toTimeStamp
)

devices_for_map <- monkeyr::get_devices_for_map(
  devices        = wrangled_devices,
  data_volume    = data_volume
)

wrangled_devices <- monkeyr::remove_excluded_devices(
  target_data    = wrangled_devices,
  data_volume    = data_volume
)

wrangled_obs <- monkeyr::remove_excluded_devices(
  target_data    = wrangled_obs,
  data_volume    = data_volume
)

nrow_vals <- nrow_values(wrangled_devices, wrangled_obs)

report_type <- "Home"

# set R options for monkey reports
monkeyr::set_options(wrangled_obs = wrangled_obs)
monkeyr::monkey_palettes(devices = wrangled_devices)

```

### Reporting period : `r date_string(params$fromTimeStamp)` - `r date_string(params$toTimeStamp)`

---
# Wait til wrangled devices avail to create title
title: "`r org_string(wrangled_devices)` Indoor Sensor Report"
---

```{r check_data, include=FALSE}
# Bail if nothing in data. Returns empty report.

if ((nrow(wrangled_devices) == 0) | (nrow(wrangled_obs) == 0)) {
  cat("No data present for the requested devices and timespan. Aborting report.")
  knitr::knit_exit("</body></html>")
}
```




## 1. Device Summary

`r device_summary_string(data_volume) `

```{r echo=FALSE}
  home_summary_kable(wrangled_devices) 
```
#### Table 1.1.   Number of properties with devices installed
<br />

```{r echo=FALSE}
  room_summary_kable(wrangled_devices) 
```
#### Table 1.2.   Summary of device locations by room type
<br />

```{r echo=FALSE} 
  device_excluded_kable(data_volume)
```
#### Table 1.3.   Summary of device locations by room type
<br />




## 2. Temperature Analysis Introduction

### 2.1   The Health Standards
Low indoor temperatures are associated with increased risks of respiratory and cardiovascular diseases. The below table summarises the impact of indoor temperature on health, and Figure 2.1.1 shows the ratio of devices by the lowest night-time temperature ever experienced during the reporting period. The night-time is defined as between 11 pm and 7 am.
<br />

```{r echo=FALSE}
who_guidance_kable()
```
#### Table 2.1.1. Impact of indoor temperature on health
<br />

### 2.2. Example Results
We will use an artificial data set to show what various homes look like - from the ideal case to homes which performs progressively more poorly. By examining the temperature data, we would like to answer the following questions:

<ol>
  <li>What are the likely health impacts in the home? By comparing the night-time temperatures experienced against the WHO guidelines.</li>
  <li>How well is the building performing? By preforming an Indoor Vs Outdoor Regression Test to see how well the building protects from the elements.</li>
  <li>What is the 'worst case' experienced in each room? By looking at the lowest temperature recorded- at night.</li>
</ol>

#### 2.2.1 Example Data Set : Likely Health Impacts
To determine the likely health impact of the home, we compare the temperature data against the WHO guidelines. In the ideal case, every home should remain above 18 °C all the time. The following example data set shows a range of scenarios from the ideal where the temperature is consistently above 18 °C to a home where the temperature falls below 12 °C for significant periods, which constitutes a potentially serious risk to children's health.



#### 2.2.2 Example Data Set : Building Performance
A linear regression analysis of night time data is used to estimate the relationship between the indoor and outdoor temperatures. The result is the ‘estimated correlation’. This can be positive, zero or negative, where a positive value indicates that the outdoor temperature is affecting the indoor temperature. The higher the estimated correlation factor, the stronger the effect. A lower estimated correlation means that the building is performing well by providing shelter from the effects of the outdoor weather.

To compare the estimated correlation for different test cases, we use box plots. The thick line across the centre of the box indicates the median value. We use the median value to reduce the impact of extreme outliers and obtain a more representative result than the mean.

To understand the correlation factor: below 0.4 is good; below 0.7 is average; below 1.0 is poor; above 1.0 is very poor. The following example plot should help to illustrates this.

```{r echo=FALSE}
section_number = 3
target_var <- "room"
mytempVarTitle <- stringi::stri_trans_totitle(target_var)
```



## `r section_number` Temerature Analysis for `r mytempVarTitle`

### `r section_number`.1 Indoor-Outdoor Corellation (`r mytempVarTitle`)

```{r  echo=FALSE}
## test
target_var <- "room"
reg_data  <- get_reg_data(wranged_devices, wrangled_obs, target_reading = "temp")
boxplot <- get_reg_boxplot(reg_data, target_var)
boxplot
```
#### Figure `r section_number`.1.1. Estimated Temperature Correlation of Indoor - Outdoor by `r mytempVarTitle` 
<br />

```{r  echo=FALSE}
reg_kable <- get_reg_kable(reg_data, target_var)
reg_kable
```
#### Figure `r section_number`.1.2. Estimated Temperature Correlation Tabulated by `r mytempVarTitle`
<br />


### `r section_number`.2 Time Spent Below The Health Standard by (`r mytempVarTitle`)

```{r echo=FALSE}
exposure_chart_data <- get_exposure_chart_data(wrangled_obs, wrangled_devices, target_var)
exposure_plot <- get_exposure_plot(exposure_chart_data, target_var)
exposure_plot
```
#### Figure `r section_number`.2.1. Percentage of night-time temperature below Threshold by (`r mytempVarTitle`) (n = `r nrow_vals$included_n`)
<br />

```{r echo=FALSE}
temp_exposure      <- get_temp_exposure(wrangled_obs, wrangled_devices, target_var)
exposure_kable_var <- get_exposure_kable_var(temp_exposure, target_var)
exposure_kable_var
```
#### Table `r section_number`.2.1. Percentage of time spent below the minimum health standard
<br />

```{r echo=FALSE}
exposure_kable_dev <- get_exposure_kable_dev(temp_exposure, target_var)
exposure_kable_dev
```
#### Table `r section_number`.2.2 Summary of all devices
<br />


### `r section_number`.3 Lowest Temperature Experienced (`r mytempVarTitle`)

```{r echo=FALSE}
lowtemp_chart_data <- get_lowtemp_chart_data(wrangled_obs, wrangled_devices, target_var)
lowtemp_chart      <- get_exposure_plot(lowtemp_chart_data, target_var)
lowtemp_chart
```
#### Figure `r section_number`.3.1 Lowest night-time temperature  ever experienced by (`r mytempVarTitle`) (n = `r nrow_vals$included_n`)
<br />

`r section_number <- section_number + 1`



