---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    social: [ "menu" ]
    # logo: !expr system.file("app/www", "logo.png", package = "monkeyr")
    # favicon: !expr system.file("app/www", "favicon.png", package = "monkeyr")
    logo: "www/logo.png"
    favicon: "www/favicon.png"
    orientation: rows

# paths with `inst` will only work in `dev` setting. 
# in `production` setting, please use real data
# or call installed files with `system.file`
# see example in `?knit_home_report()`
params:
  filtered_obs:             "../test-data/monkey_a/obs.csv"
  filtered_weather:         "../test-data/monkey_a/weather.csv"
  filtered_devices:         "../test-data/monkey_a/dev.csv"
  filtered_interventions:   "../test-data/monkey_a/interv.csv"
  report_params:            "-map-"                                            
  fromTimeStamp:            1627639151
  toTimeStamp:              1630317551
---

```{r}
ENABLE_DEBUG <- FALSE
```


```{r setup }
# load monkeyr package
library(monkeyr)
library(dplyr)
library(magrittr)

# other dependencies loaded through namespace
```

```{r wrangle_data }
# generate tables and values used later in the report

wrangled_devices <- wrangle_devices(params$filtered_devices)

wrangled_weather <- wrangle_weather(params$filtered_weather)


wrangled_obs <- wrangle_observations(
  filtered_obs = params$filtered_obs,
  devices = wrangled_devices,
  weather = wrangled_weather
)

data_volume <- get_data_volume(
  observations = wrangled_obs,
  from_timestamp = params$fromTimeStamp,
  to_timestamp = params$toTimeStamp
)

devices_for_map <- get_devices_for_map(
  devices = wrangled_devices,
  data_volume = data_volume
  )

wrangled_devices <- remove_excluded_devices(
  target_data = wrangled_devices,
  data_volume = data_volume
)

wrangled_obs <- remove_excluded_devices(
  target_data = wrangled_obs,
  data_volume = data_volume
)

nrow_vals <- nrow_values(wrangled_devices, wrangled_obs)

report_type <- "Home"

# set R options for monkey reports
set_options(observations = wrangled_obs)
monkey_palettes(devices = wrangled_devices)
```

---
title: "`r report_type ` Report"
---

```{r check_data, results = "hide"}

# Bail if nothing in data. Returns empty report.
if ((nrow(wrangled_devices) == 0) | (nrow(wrangled_obs) == 0)) {
  cat("No data present for the requested devices and timespan. Aborting report.")
  knitr::knit_exit("</body></html>")
}

```

# Healthy Homes Performance {data-icon="fa-chart-bar"}

## Column 1

### Performance Against World Health Organisation Guidelines

```{r}
who_chart <- who_threshold_data(observations = wrangled_obs) %>%
 who_threshold_chart(from_timestamp = params$fromTimeStamp, params$toTimeStamp)
who_chart
```

### World Health Organisation Guidelines

Low indoor temperatures are associated with increased risks of respiratory and cardiovascular diseases. The below table summarises the impact of indoor temperature on health, and the graph opposite shows the the percentage of time each of your rooms spends below each of the temperature thresholds defined. He Kainga Oranga recommends that we look at night time temperatures when we are considering health impact. The night-time is defined as between 11 pm and 7 am.

----------

```{r}
who_guidance_kable()
```

----------

## Column 2

### Hours each night below 18 °C

```{r}
totals <-
  who_threshold_data(observations = wrangled_obs) %>%
  get_who_totals()

below_12 <- totals$below_12
below_16 <- totals$below_16
below_18 <- totals$below_18

palette <- get_heat_palette(6)

flexdashboard::valueBox(paste0(round(8 * below_18, 1), " hrs (",scales::percent(below_18),")"),
                        icon = "fa-thermometer-half",
                        # color = ifelse(below_18 > 0.40, "warning", "primary"),
                        color = palette[4])
```

### Hours each night below 16 °C

```{r}
flexdashboard::valueBox(paste0(round(8 * below_16, 1) , " hrs (", scales::percent(below_16), ")"),
                        icon = "fa-thermometer-quarter",
                        # color = color = ifelse(below_16 > 0.20, "warning", "primary")
                        color = palette[5])
```

### Hours each night below 12 °C

```{r}
flexdashboard::valueBox(paste0(
  round(8 * below_12, 1) ,
  " hrs (",
  scales::percent(below_12),
  ")"
),
icon = "fa-thermometer-empty",
# color = ifelse(below_12 > 0.01, "danger", "primary")
color = palette[6])
```


# Raw Timeseries Data {data-icon="fa-chart-line"}

## Column 1 {.tabset}

### Temperature

```{r}
# if (getOption("TEMP_ENABLE")) {
ts_chart(
  observations = wrangled_obs,
  from_timestamp = test_params()$fromTimeStamp,
  to_timestamp = test_params()$toTimeStamp,
  target_variable = "temp"
)
# }
```

### Humidity

```{r}
ts_chart(
  observations = wrangled_obs,
  from_timestamp = test_params()$fromTimeStamp,
  to_timestamp = test_params()$toTimeStamp,
  target_variable = "hum"
)
```

## Column 2

### Highest Ever Temperature

```{r}
extremes_temp <- get_extreme_vals(
  observations = wrangled_obs,
  target_variable = "temp")

flexdashboard::valueBox(extremes_temp$highest_val,
         icon = "fa-thermometer-full",
         color = ifelse(extremes_temp$highest_val > 29, "warning", "primary"))
```

### Lowest Ever Temperature

```{r}
flexdashboard::valueBox(extremes_temp$lowest_val,
         icon = "fa-thermometer-empty",
         color = ifelse(extremes_temp$lowest_val < 12, "warning", "primary"))
```

### Mean Termperature

```{r}
flexdashboard::valueBox(extremes_temp$mean_val,
         icon = "fa-thermometer-half",
         color = ifelse(extremes_temp$mean_val < 16, "warning", "primary"))
```


