---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    social: [ "menu" ]
    logo: !expr system.file("app/www", "logo.png", package = "monkeyr")
    favicon: !expr system.file("app/www", "favicon.png", package = "monkeyr")
    # logo: "../www/logo.png"
    # favicon: "../www/favicon.png"
    orientation: rows
    pandoc_args: [
      "+RTS", "-K16m",
      "-RTS"
    ]

# paths with `inst` will only work in `dev` setting. 
# in `production` setting, please use real data
# or call installed files with `system.file`
# see example in `?knit_report()`
params:
  filtered_obs:             "../dummy-data/monkey_c/obs.csv"
  filtered_weather:         "../dummy-data/monkey_c/weather.csv"
  filtered_devices:         "../dummy-data/monkey_c/dev.csv"
  filtered_interventions:   "../dummy-data/monkey_c/interv.csv"
  report_params:            "-map-"                                            
  fromTimeStamp:            1681420822
  toTimeStamp:              1681766422
---

```{r}
ENABLE_DEBUG <- FALSE
```


```{r setup }
  ## load monkeyr package
  library(monkeyr)
  library(dplyr)
  library(magrittr)
  library(fontawesome)
  # use fontawesome::fa_metadata() to see avail icons!

## other dependencies loaded through namespace
```

```{r wrangle_data}

  ## STANDARD DATA WRANGLING & JOINING
  ## ---------------------------------
  
  tryCatch(
    {
      wrangled_devices <- monkeyr::wrangle_devices(params$filtered_devices)
      
      # fudge to generate WISE devices
      # wrangled_devices <- wrangled_devices %>%
      #   dplyr::filter(grepl("Whipit", cluster, fixed = TRUE))
      #   dplyr::filter(grepl("HPA/Whipit", cluster, fixed = TRUE))
      
      
      # local_tz         <- monkeyr::get_local_tz(wrangled_devices)
    
      wrangled_weather <- monkeyr::wrangle_weather(params$filtered_weather)
      
      # start_time <- Sys.time()
      wrangled_obs <- monkeyr::wrangle_observations(
        filtered_obs   = params$filtered_obs,
        devices        = wrangled_devices,
        weather        = wrangled_weather
      )
      # end_time <- Sys.time()
      # end_time - start_time
      
      data_volume <- monkeyr::get_data_volume(
        observations   = wrangled_obs,
        from_timestamp = params$fromTimeStamp,
        to_timestamp   = params$toTimeStamp
      )
      
      devices_for_map <- monkeyr::get_devices_for_map(
        devices        = wrangled_devices,
        data_volume    = data_volume
      )
      
      wrangled_devices <- monkeyr::remove_excluded_devices(
        target_data    = wrangled_devices,
        data_volume    = data_volume
      )
      
      wrangled_obs <- monkeyr::remove_excluded_devices(
        target_data    = wrangled_obs,
        data_volume    = data_volume
      )
      
      sample_rate <- ceiling(nrow(wrangled_obs)/50000)
      if (sample_rate > 1) {
        wrangled_obs <- monkeyr::downsample_obs(wrangled_obs, sample_rate)
      }
      
      nrow_vals <- nrow_values(wrangled_devices, wrangled_obs)
      
      report_type <- "Home"
      
      ## set R options for monkey reports
      monkeyr::set_options(wrangled_obs = wrangled_obs)
     # monkeyr::monkey_palettes(devices = wrangled_devices) # doesn't work - use get_palettes instead
      unique_readings <- monkeyr::unique_readings(wrangled_obs = wrangled_obs)
    },
    error = function(cond) {
      monkeyr::monkey_knit_error(err = cond, resource = "wrangle_data")
    }
  )
```

---
title: "`r report_type ` Report"
---

```{r check_data, results='asis'}
  ## Bail if nothing in weather. Means user hasn't entered any address data.
  if ( is.null(wrangled_weather) ) { ## We agressively set it to NULL in wrangle_weather!
    cat("Hi There!\n\n The monkey-report-generator wasn't able to link up with our outdoor weather database. Could you check that you have added address information for your devices before trying again. We need to know what region you are in to get representative outdoor data. \n\nAborting report.")
    knitr::knit_exit("</body></html>")
  }
  ## Bail if nothing in data. Returns empty report.
  if ((nrow(wrangled_devices) == 0) | (nrow(wrangled_obs) == 0)) {
    cat("No data present for the requested devices and timespan. Aborting report.")
    knitr::knit_exit("</body></html>")
  }
```



<!-- PAGE 1: HEALTHY HOMES    -->
<!-- ------------------------ -->

# Healthy Homes Performance {data-icon="fa-chart-bar"}

## Column 1

### Performance Against World Health Organisation Guidelines

```{r}
  who_chart <- 
    monkeyr::who_threshold_data(observations = wrangled_obs) %>%
    monkeyr::who_threshold_chart(from_timestamp = params$fromTimeStamp, to_timestamp = params$toTimeStamp)
  
  who_chart
```

### World Health Organisation Guidelines

Low indoor temperatures are associated with increased risks of respiratory and cardiovascular diseases. The below table summarises the impact of indoor temperature on health, and the graph opposite shows the the percentage of time each of your rooms spends below each of the temperature thresholds defined. He Kainga Oranga recommends that we look at night time temperatures when we are considering health impact. The night-time is defined as between 11 pm and 7 am.

----------

```{r}
  who_guidance_kable()
```

----------

## Column 2

### Hours each night below 18 °C

```{r}
  totals <-
    monkeyr::who_threshold_data(observations = wrangled_obs) %>%
    monkeyr::get_who_totals()
  
  below_12 <- totals$below_12
  below_16 <- totals$below_16
  below_18 <- totals$below_18
  
  palette <- monkeyr::get_heat_palette(6)
  
  flexdashboard::valueBox(paste0(round(8 * below_18, 1), " hrs (",scales::percent(below_18),")"),
                          icon = "fa-thermometer-half",
                          # color = ifelse(below_18 > 0.40, "warning", "primary"),
                          color = palette[4])
```

### Hours each night below 16 °C

```{r}
  flexdashboard::valueBox(paste0(round(8 * below_16, 1) , " hrs (", scales::percent(below_16), ")"),
                        icon = "fa-thermometer-quarter",
                        # color = color = ifelse(below_16 > 0.20, "warning", "primary")
                        color = palette[5])
```

### Hours each night below 12 °C

```{r}
  flexdashboard::valueBox(paste0(
    round(8 * below_12, 1) ,
    " hrs (",
    scales::percent(below_12),
    ")"
  ),
  icon = "fa-thermometer-empty",
  # color = ifelse(below_12 > 0.01, "danger", "primary")
  color = palette[6])
```


<!-- PAGE 2: VENTILATION CODE -->
<!-- ------------------------ -->
```{r, echo=FALSE, results='asis'}
  if ("co2" %in% wrangled_obs$reading) {
    res <- knitr::knit_child('ventilation.rmd', quiet = TRUE)
    cat(res, sep = '\n')
  }
```


<!-- PAGE 3: PM CODE -->
<!-- --------------- -->
```{r, echo=FALSE, results='asis'}
  if ("pm2_5" %in% wrangled_obs$reading) {
    res <- knitr::knit_child('pm.rmd', quiet = TRUE)
    cat(res, sep = '\n')
  }
```


<!-- PAGE 4: HCHO CODE -->
<!-- --------------- -->
```{r, echo=FALSE, results='asis'}
  if ("hcho" %in% wrangled_obs$reading) {
    res <- knitr::knit_child('hcho.rmd', quiet = TRUE)
    cat(res, sep = '\n')
  }
```


<!-- PAGE 5: TIME SERIES CODE -->
<!-- ------------------------ -->

# `r fa("chart-line", fill = "white")`  Raw Timeseries Data

## Column 1 {.tabset}

### Temperature

```{r}
  if (getOption("temp")) {
    monkeyr::ts_chart(
      observations = wrangled_obs,
      from_timestamp = params$fromTimeStamp,
      to_timestamp = params$toTimeStamp,
      target_variable = "temp"
    )
  } else {
    cat("No Temperature Data Available!")
  }
```

### Humidity

```{r}
  if (getOption("hum")) {
    monkeyr::ts_chart(
      observations = wrangled_obs,
      from_timestamp = params$fromTimeStamp,
      to_timestamp = params$toTimeStamp,
      target_variable = "hum"
    ) 
  } else {
    cat("No Humidity Data Available!")
  }
```

```{r echo=FALSE, results="asis"}

  ## All the rest are present when data is available!
  ## ------------------------------------------------
  
  valid_readings <- monkeyr::filter_list(unique_readings, permitted_readings())
  valid_readings <- valid_readings[valid_readings != "temp"]
  valid_readings <- valid_readings[valid_readings != "hum"]
  
  if (length(valid_readings) > 0) {
    plotlist = list()
    for (i in 1 : length(valid_readings)) {
      cat("\n", "\n### ", toupper(valid_readings[i]), "\n")
      ts_chart <- monkeyr::ts_chart(
        observations = wrangled_obs,
        from_timestamp = params$fromTimeStamp,
        to_timestamp = params$toTimeStamp,
        target_variable = valid_readings[i]
      ) 
      
      plotlist[[2*i]] = ts_chart
      print(htmltools::tagList(ts_chart))
      plotlist[[2*i+1]] = ts_chart
      print(htmltools::tagList(ts_chart))
    }
  }
```


## Column 2

### Highest Ever Temperature

```{r}
  extremes_temp <- monkeyr::get_extreme_vals(
    observations = wrangled_obs,
    target_variable = "temp")
  
  flexdashboard::valueBox(extremes_temp$highest_val,
           icon = "fa-thermometer-full",
           color = ifelse(extremes_temp$highest_val > 29, "warning", "primary"))
```

### Lowest Ever Temperature

```{r}
  flexdashboard::valueBox(extremes_temp$lowest_val,
         icon = "fa-thermometer-empty",
         color = ifelse(extremes_temp$lowest_val < 12, "warning", "primary"))
```

### Mean Temperature

```{r}
  flexdashboard::valueBox(extremes_temp$mean_val,
         icon = "fa-thermometer-half",
         color = ifelse(extremes_temp$mean_val < 16, "warning", "primary"))
```
