---
title: "Raw and Metadata Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    social: [ "menu" ]
    logo: !expr system.file("app/www", "logo.png", package = "monkeyr")
    favicon: !expr system.file("app/www", "favicon.png", package = "monkeyr")
    # logo: "../www/logo.png"
    # favicon: "../www/favicon.png"
    orientation: rows
    pandoc_args: [
      "+RTS", "-K16m",
      "-RTS"
    ]

# paths with `inst` will only work in `dev` setting. 
# in `production` setting, please use real data
# or call installed files with `system.file`
# see example in `?knit_report()`
params:
  filtered_obs:             "../dummy-data/co2_demo/obs.csv"
  filtered_weather:         "../dummy-data/co2_demo/weather.csv"
  filtered_devices:         "../dummy-data/co2_demo/dev.csv"
  filtered_interventions:   "../dummy-data/co2_demo/interv.csv"
  report_params:            "-map-"  
  fromTimeStamp:            1682282766
  toTimeStamp:              1682887566
---

```{r}
ENABLE_DEBUG <- FALSE
```


```{r setup }
  ## load monkeyr package
  library(monkeyr)
  library(dplyr)
  library(magrittr)
  library(fontawesome)
  library(hrbrthemes)
  library(ggplot2)
  # use fontawesome::fa_metadata() to see avail icons!

## other dependencies loaded through namespace
```





<!-- RAW DATA LINKS   -->
<!-- ---------------- -->

# Raw data Download {data-icon="fa-save-ol"}

## Column 1 {data-height=150}

```{r setup_downloads}
  ## https://cran.r-project.org/web/packages/downloadthis/vignettes/downloadthis.html
  library(downloadthis)

# Empty dataframe for when there is no data
  empty_df <- data.frame(
    "Unicorn_Name" = c(
      "Sparkle", 
      "Rainbow", 
      "Starlight", 
      "Twilight", 
      "Moonbeam"
    ),
    "Favorite_Food" = c(
      "Glitter Grapes", 
      "Sunshine Strawberries", 
      "Dreamy Donuts", 
      "Magical Macarons", 
      "Stardust Spaghetti"
    ),
    "Hobby" = c(
      "Cloud Racing", 
      "Star Gazing", 
      "Rainbow Painting", 
      "Dream Weaving", 
      "Moon Dancing"
    ),
    stringsAsFactors = FALSE
  )

```

```{css}
.button_green {
  background: #B7DFCB;
  color: black;
  width: 50%;
  font-size: 32px;
  
  border-style: solid;
  border-color: white;
  border-radius: 10px;
  border-width: 5px;
}
.button_light {
  background: #5ABAD1;
  color: black;
  width: 50%;
  font-size: 32px;
  
  border-style: solid;
  border-color: white;
  border-radius: 10px;
  border-width: 5px;
}
.button_medium {
  background: #3984B6;
  color: white;
  width: 50%;
  font-size: 32px;
  
  border-style: solid;
  border-color: white;
  border-radius: 10px;
  border-width: 5px;
}
.button_dark {
  background: #275a7c;
  color: white;
  width: 50%;
  font-size: 32px;
  
  border-style: solid;
  border-color: white;
  border-radius: 10px;
  border-width: 5px;
}
```

```{r downloads_1}
  raw_devices <- monkeyr::wrangle_devices(params$filtered_devices)

  if (is.null(raw_devices)) {
    raw_devices <- empty_df
  }

  raw_devices %>%
    download_this(
      output_name = "devices",
      output_extension = ".csv",
      button_label = "Devices",
      button_type = "primary",
      has_icon = TRUE,
      icon = "fa fa-save",
      class = "button_dark"
  )
  
  raw_weather <- monkeyr::wrangle_weather(params$filtered_weather)
  
  if (is.null(raw_weather)) {
    raw_weather <- empty_df
  }
  
  raw_weather %>%
    download_this(
      output_name = "weather",
      output_extension = ".csv",
      button_label = "Weather",
      button_type = "primary",
      has_icon = TRUE,
      icon = "fa fa-save",
      class = "button_medium"
  )
```

## Column 2 {data-height=150}

```{r downloads_2}
  raw_observations <- readr::read_csv(params$filtered_obs, col_types = "ciiicd")

  if (is.null(raw_observations)) {
    raw_observations <- empty_df
  }

  raw_observations %>%
    download_this(
      output_name = "observations",
      output_extension = ".csv",
      button_label = "Observations",
      button_type = "primary",
      has_icon = TRUE,
      icon = "fa fa-save",
      class = "button_green"
  )
  
  raw_interventions <- readr::read_csv(params$filtered_interventions, col_types = "cicic")
  
  if (is.null(raw_interventions)) {
    raw_interventions <- empty_df
  }
  
  raw_interventions %>%
    download_this(
      output_name = "interventions",
      output_extension = ".csv",
      button_label = "Interventions",
      button_type = "primary",
      has_icon = TRUE,
      icon = "fa fa-save",
      class = "button_light"
    )
```



## Tools {.tabset}

### RStudio

#### Installation

Install the latest development version of monkeyr from github :

```{r, eval = FALSE, echo=TRUE}
devtools::install_github("monkeytronics/monkeyr", build_vignettes = TRUE)
```

Monkeyr is structured as pure functions. The library dependencies are listed in the
`DESCRIPTION` file. This along with `roxygen` creates the `NAMESPACE` with all imports/exports.

#### Example Set Up of an Rmd File (using home report example)

We start with a Monkeytronics Sensor Node data set :\cr

* `obs.csv`
* `dev.csv`
* `weather.csv`
* `interv.csv`

And we use the wrangling functions to create the following sanitised, wrangled data :

* `wrangled_obs`     : the joined data set
* `wrangled_devices` : devices list minus excluded devices
* `devices_for_map`  : a list used to populate a deployment map

```{r, eval = FALSE, echo=TRUE}
library(monkeyr)

wrangled_devices <- wrangle_devices(params$filtered_devices)

wrangled_weather <- wrangle_weather(params$filtered_weather)

wrangled_obs    <- wrangle_observations(
  filtered_obs   = params$filtered_obs,
  devices        = wrangled_devices,
  weather        = wrangled_weather
)

data_volume     <- get_data_volume(
  observations   = wrangled_obs,
  from_timestamp = params$fromTimeStamp,
  to_timestamp   = params$toTimeStamp
)

devices_for_map <- get_devices_for_map(
  devices        = wrangled_devices,
  data_volume    = data_volume
)

wrangled_devices<- remove_excluded_devices(
  target_data    = wrangled_devices,
  data_volume    = data_volume
)

wrangled_obs    <- remove_excluded_devices(
  target_data    = wrangled_obs,
  data_volume    = data_volume
)
```


### Python

We haven't got any code yet for python users. If you've got any you'd like to share to help other users, we'd be most grateful!

### Excel

We haven't got any code yet for excel users. If you've got any you'd like to share to help other users, we'd be most grateful!








